Sampling requirements to detect ecosystem change

### 2020-04-01 R/manuscript_draft.Rmd
adding arkilanian etal 2020 paper

Our approach is applicable to a wide range of systems and questions, but it does have limitations. When less resources are needed for sample analysis, as opposed to collection, investigators will likely be able to process every sample. When sample analysis costs are high, then regular and iterative sampling are better than random sampling (Figs. \ref{fig:simulation_approaches_plot},S2,S3). In addition, some questions require a continuous time series, or at least a regular sampling interval. For example, continuous subsampling of a time-series is required to detect critical slowing-down or early warning of shifts [@Frossard2015;@Doncaster2016]. However, critical slowing down does not necessarily result in a shift, and a shift can occur without critical slowing down [@Spears2017]. Signs of critical slowing downs are important to understand and recognize because they provide potential early warnings [@Doncaster2016], but in terms of management, knowing the timing of a shift can have larger implication in addressing the driver. Thus, selecting a set number of samples or specific approach may also limit what future questions can be asked. However, more samples could be processed later to address these additional questions.

>>>>

Our approach is applicable to a wide range of systems and questions, but it does have limitations. When less resources are needed for sample analysis, as opposed to collection, investigators will likely be able to process every sample. When sample analysis costs are high, then regular and iterative sampling are better than random sampling (Figs. \ref{fig:simulation_approaches_plot},S2,S3). In addition, some questions require a continuous time series, or at least a regular sampling interval. For example, continuous, high-resolution subsampling of a time-series is generally required to detect critical slowing-down or early warning of shifts [@Frossard2015; @Doncaster2016], although recent work suggest that combining indicators (in the specific study, trait dynamics and abundance-based early warning signals) allows to forecast population collapse even with at lower resolution and time-series length [@arkilanian_effect_nodate]. Extending on the question of being able to detect early warning signals, this objective must be weighed in with the ultimate goal: detecting ecosystem shift. Critical slowing down does not necessarily result in a shift, and a shift can occur without critical slowing down [@Spears2017]. Signs of critical slowing downs are important to understand and recognize because they provide potential early warnings [@Doncaster2016], but in terms of management, knowing the timing of a shift can have larger implication in addressing the driver. Thus, selecting a set number of samples or specific approach may also limit what future questions can be asked. Finally, more subsamples could be processed later to address additional questions.
